% !TEX root = ../thesis.tex

\begin{abstract}
内存保护是计算机安全中的重要组成部分，针对内存的攻击被划分为软件攻击与硬件攻击，软件攻击可以通过内存隔离防御，而硬件攻击需要通过内存加密与完整性保护来防御。
内存隔离和加密在计算机系统与安全中都有较为成熟的解决方式，但是内存完整性保护还面临着内存大小与性能之间的权衡。2016英特尔推出了Software Guard Extensions（SGX），
SGX能够实现内存隔离，加密与完整性保护，从而为enclave程序提供了可信执行环境。虽然SGX提供了强安全保障机制，但是enclave能够使用的内存仅仅只有128M，受限于内存的完整性保护。

在本文中，提出了一种新颖的可扩展内存完整性保护方案：挂载式完整性保护树。它能够保护TB级别的内存数据，实现离散的内存保护与动态的安全内存分配。同时，我们为完整性保护树提供了动态原语：挂载与卸载，以代替
SGX中采用的页交换机制，实现了可扩展的内存保护。

我们在gem5上实现了可挂载完整性保护树的原型，并且在SPECCPU上做了初步的测试。测试的结果表明，采用了可挂载完整性保护树相较于之前先进的VAULT和SIT提升了2\sim3
倍的性能，在极限的场景下能够提升7\sim8倍的性能。可挂载完整性保护树为可信执行环境，非易失性内存等新兴的应用场景与硬件提供了强安全保障，弥补了内存保护中，完整性保护的缺陷。

\end{abstract}

\begin{enabstract}
  Memory protection is an important part of computer security. Attacks against memory are divided into software attacks and hardware attacks. Software attacks can be defended by memory isolation, while hardware attacks need to be defended by memory encryption and integrity protection.

  Memory isolation and encryption have relatively mature solutions in computer systems and security, however memory integrity protection still face the trade-off between memory size and performance. In 2016, Intel launched the Software Guard Extensions (SGX), SGX enables memory isolation, encryption, and integrity protection, which provides a trusted execution environment for enclave. However although SGX provides strong security mechanism, enclave can only use 128M for memory, which is limited by memory integrity protection.
  
  In this paper, a novel scalable memory integrity protection scheme is proposed: Mountable Merkle tree (MMT), which can protect TB level memory data and realize discrete memory protection and dynamic secure memory allocation. At the same time, we provide dynamic primitives for integrity protection trees: mount and unmount, which can significantly improve the performance against the page swapping mechanism adopted in SGX. We implement a prototype of a mountable merkle tree on gem5 and do the preliminary testing on SPECCPU. The results of the tests show that using the mountable merkle tree can improve 2 to 3 times better performance compared to VAULT and SIT, and 7 to 8 times performance improvement in the extreme scenarios. Mount Merkle tree can provide robust memory security protection for the trusted execution environment, 
  non-volatile memory and other emerging scenarios and new hardware, and make up the integrity protection defects in traditional memory protection.
\end{enabstract}
